Network Fusion through CDRP Model\\ Decomposition and Assembly

### 2020-01-08 paper/paper.tex
write begining of section 3 and some guideline

The table in Figure~\ref{fig:assemble-example-encoding} shows the encoding mentioned in the certificate algorithm.
If we only use the encoding from $d_1, d_2, d_3$, we find no two subclasses with different labels share the same encoding, and therefore certify the correctness of the feasible solution proposed before.
For the partial classification task for $A_3$, using two bits from $d_2, d_4$ already provides distinguishable encoding for $A_{31}$ and the remaining dummy classes.

@@

The search is guided by the residual entropy of target subclasses and dummy subclasses.
\begin{equation}
	H(C) = \sum_{c \in C} p(c)H(c) = \sum_{c \in C} p(c)\sum_{l \in \mathcal{L}'} p(c, l)\log\frac{1}{p(c, l)}
\end{equation}

\section{Model Assembly based on CDRP Decomposition and Clustering}
\label{sec:cdrp}
\subsection{Critical Data Routing Path Model}
\subsection{CDRP Model Clustering}
\subsection{CDRP Model Assembly}

\section{Experiments}
\subsection{CDRP Models of VGGNet and ? trained on CIFAR-100}
\subsection{Fusing VGGNet and ? for Specific Tasks through CDRP Assembly}

>>>>

The table in Figure~\ref{fig:assemble-example-encoding} shows the encoding mentioned in the certificate algorithm for the intro example in Figure~\ref{fig:assemble-example-venn}.
If we only use the encoding from $d_1, d_2, d_3$, we find no two subclasses with different labels share the same encoding, and therefore certify the correctness of the feasible solution proposed before.
For the partial classification task for $A_3$, using two bits from $d_2, d_4$ already provides distinguishable encoding for $A_{31}$ and the remaining dummy classes.

@@

The search is guided by the residual entropy \eqref{eq:entropy} of target subclasses and dummy subclasses.
\begin{equation}
	H(C) = \sum_{c \in C} p(c)H(c) = \sum_{c \in C} p(c)\sum_{l \in \mathcal{L}'} p(c, l)\log\frac{1}{p(c, l)}
	\label{eq:entropy}
\end{equation}
where $p(c)$ is the probability for encoding $c$ to occur, and $p(c, l)$ is the probability of a sample having encoding $c$ and label $l$.
Note that the label ranges over $\mathcal{L}'$, the set of target labels and one dummy label, and all labels that are not target is defined to be equal to the dummy one.
In each search iteration, the algorithm will choose the classifier set that minimizes the entropy greedily, so that the search could possibly to end with minimum search depth.

\todo{Analysis}

\section{Model Assembly based on CDRP Decomposition and Clustering}
\label{sec:cdrp}
In \cref{sec:assembly}, we have formalized the problem and proposed a general algorithm searching for a feasible solution to a search problem instance.
In this section, we want to instantiate the assembly problem in a concrete setting.
To do so, we need to find an efficient way to generate the input to the problem.
More specifically, we need to find an initial set of binary classifiers with following constrains.
\begin{itemize}
	\item The initial set should guarantee at least one feasible solution for some $k$.
	\item There should exist overlapping subclasses among classifiers to allow multiple choices, i.e., allow removing of redundant feature extractors.
	\item We can not train a large set of binary classifiers from scratch, because it takes too many prior knowledge and time to get an initial set that have feasible solution with the space for improvements.
\end{itemize}

\paragraph{Remark.} We do not need to provide the subclasses in the input, because they can be derived from the initial set of classifiers.
Given encodings under the initial classifier set, samples share the same encoding can be considered as a subclass, and there is no need to further split those subclasses.
For example, in the intro example in Figure~\ref{fig:assemble-example-venn}, there is no need to distinguish $A_{11}$ and $A_{12}$ and we can group them as a single subclass.

To satisfy the above constraints, we follow the previous work of Wang \textit{et al.} \cite{wang2018interpret} to use critical data routing path (CDRP) for generating the input.
CDRP clustering allow us to decompose a large network model into several disjoint small ones.
To have overlapping classifiers, we decompose two different networks on the same dataset and fine tuning the CDRP models into binary classifiers.
We use image classification task on CIFAR-100 and VGG16 of type C and D for demonstration.

\subsection{CDRP Decomposition and Clustering}
Guideline:
\begin{itemize}
	\item How to train gates, the functionality of the gates, how to interpret gate weight (lambda) feature of samples (similar to original paper)
	\item How to get decomposed classifiers: clustering
	\item Why clustered CDRP models might work (PCA visualization demonstration) (not performance analysis, inference experiments later)
	\item Why fine tuning the clustered CDRP model into binary classifiers, and how we fine tune them
\end{itemize}

\subsection{CDRP Model Assembly}

\section{Experiments}
\subsection{Verifying CDRP Models of VGGNets trained on CIFAR-100}
\subsection{Fusing VGGNets for Specific Tasks through CDRP Assembly}
